News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-05 rupnik2015.tex
paragraph added to intro

The term event is vague and ambiguous, but for the practical purposes, we define it as ``any significant happening that is being reported about in the media.'' Examples of events would include shooting down of the Malaysia Airlines plane over Ukraine on July 18th, 2014 and HSBC's admittance of aiding their clients in tax evasion on February 9th, 2015 (Figure \ref{fig:event2}). Events such as these are covered by many articles and the question is how to find all the articles in different languages that are describing a single event.

@@

@@

As input we consider a high volume of articles in different languages. By using a language detector the stream is split into separate monolingual streams. Within each monolingual stream, an online clustering approach is employed, where tracked clusters correspond to our definition of events - this is based on the Event Registry system \shortcite{Leban2014W,Leban2014I}. Our main goal in this paper is to connect such clusters (representations of events) across languages, that is, to detect that a set of articles in language $A$ reports on the same event as a set of articles in language $B$.

>>>>

The term event is vague and ambiguous, but for the practical purposes, we define it as ``any significant happening that is being reported about in the media.'' Examples of events would include shooting down of the Malaysia Airlines plane over Ukraine on July 18th, 2014 and HSBC's admittance of aiding their clients in tax evasion on February 9th, 2015 (Figure \ref{fig:event2}). Events such as these are covered by many articles and the question is how to find all the articles in different languages that are describing a single event. Generally, events are more specific than general themes as the time component plays an important role -- for example, the two wars in Iraq would be considered as separate events.

@@

The goal of this work is to examine how well events can be tracked in a multilingual reporting environment. Since this, represents complicated pipeline, we concentrate on two specific elements, namely multilingual similarity of articles and event linking using this similarity. Overall, these should be considered from a systems perspective (considering the system as a whole) rather than considering these problems in isolation.

@@

 We consider a high volume of articles in different languages. By using a language detector the stream is split into separate monolingual streams. Within each monolingual stream, an online clustering approach is employed, where tracked clusters correspond to our definition of events - this is based on the Event Registry system \shortcite{Leban2014W,Leban2014I}. Our main goal in this paper is to connect such clusters (representations of events) across languages, that is, to detect that a set of articles in language $A$ reports on the same event as a set of articles in language $B$.
